Continuous developmental change explains discontinuities in word learning

### 2020-03-21 journal/ms_blind.Rmd
more revisions

We report data from $N=$ `r N_good_ch` children ages 4-5 years from a nursery school. An additional $N=$ `r N_all_ch-N_good_ch` children participated but were removed from analyses using a preregistered exclusion criterion of not being above chance on the catch trials.\footnote{The number of children who were excluded is a bit high for this age group. This is partly due to our adoption of a 2x2 fully within-subject design, which is relatively novel for preschoolers. The length of this procedure was demanding for children, but we adopted this design based on pilot testing that indicated that precision of measurement was critical for testing our experimental predictions.} We also report data from $N=$ `r N_good_ad` adult participants tested on Amazon Mechanical Turk. An additional $N=$ `r N_all_ad-N_good_ad` were tested but removed from analyses using preregistered exclusion criteria of either having a low score on the catch trials or being familiar with the non-English sound stimuli we used in the adult experiment.

>>>>

We report data from $N=$ `r N_good_ch` children ages 4-5 years from a nursery school. An additional $N=$ `r N_all_ch-N_good_ch` children participated but were removed from analyses using a preregistered exclusion criterion of not being above chance on the catch trials.\footnote{The number of children who were excluded is a bit high for this age group. This is partly due to our adoption of a 2x2 fully within-subject design, which is relatively novel for preschoolers, and which was demanding for children. As we explain below, we adopted this design based on pilot testing that indicated that precision of measurement was critical for testing our experimental predictions.} We also report data from $N=$ `r N_good_ad` adult participants tested on Amazon Mechanical Turk. An additional $N=$ `r N_all_ad-N_good_ad` were tested but removed from analyses using preregistered exclusion criteria of either having a low score on the catch trials or being familiar with the non-English sound stimuli we used in the adult experiment.

### 2020-03-21 journal/ms_blind.tex
more revisions

We report data from \(N=\) 63 children ages 4-5 years from a nursery school. An additional \(N=\) 39 children participated but were removed from analyses using a preregistered exclusion criterion of not being above chance on the catch trials.\footnote{The number of children who were excluded is a bit high for this age group. This is partly due to our adoption of a 2x2 fully within-subject design, which is relatively novel for preschoolers. The length of this procedure was demanding for children, but we adopted this design based on pilot testing that indicated that precision of measurement was critical for testing our experimental predictions.} We also report data from \(N=\) 74 adult participants tested on Amazon Mechanical Turk. An additional \(N=\) 26 were tested but removed from analyses using preregistered exclusion criteria of either having a low score on the catch trials or being familiar with the non-English sound stimuli we used in the adult experiment.

>>>>

We report data from \(N=\) 63 children ages 4-5 years from a nursery school. An additional \(N=\) 39 children participated but were removed from analyses using a preregistered exclusion criterion of not being above chance on the catch trials.\footnote{The number of children who were excluded is a bit high for this age group. This is partly due to our adoption of a 2x2 fully within-subject design, which is relatively novel for preschoolers, and which was demanding for children. As we explain below, we adopted this design based on pilot testing that indicated that precision of measurement was critical for testing our experimental predictions.} We also report data from \(N=\) 74 adult participants tested on Amazon Mechanical Turk. An additional \(N=\) 26 were tested but removed from analyses using preregistered exclusion criteria of either having a low score on the catch trials or being familiar with the non-English sound stimuli we used in the adult experiment.
